Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Use 'omit' in explanation of rendering volume behind intersection in first approach

Next the part of the volume behind the intersection is rendered into the results
texture.  To get just that part the back faces of the Boolean AND are used
instead of the front faces of the cube.  Note in the code snippet below we only
show the first volume, hide where we set the uniform variables in the shader
program for brevity, and give the intersection an ID so it can be redrawn later.

>>>>

Next the part of the volume behind the intersection is rendered into the results
texture.  To get just that part the back faces of the Boolean AND are used
instead of the front faces of the cube.  Note in the code snippet below we omit
the instructions for rendering the second volume and for setting uniform
variables.  We also give the intersection an ID so it can be redrawn later.
